Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-15 writeup/rocha_etal.tex
Fixes typo

\cite{dasaro1978} showed that the velocity of linear internal waves
in the mixed layer strongly depends on the density jump at the mixed-layer
base, with largest mixed layer velocities when the jump is strongest.
In summer, the shallow mixed layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed-layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape of the baroclinic modes
changes seasonally. In particular the baroclinic modes are
significantly more surface intensified in late summer/early fall
 (supplemental material).
If the internal wave source has weak seasonal dependence, then a strong
seasonal cycle in the near-surface expression of internal waves is expected.
Internal tide generation does not show a seasonal modulation \citep[e.g.,][]{alford2003},
and therefore one expects a strong seasonality in the near-surface
expression of internal tides and
other submesoscale inertia-gravity waves generated through internal tide interactions.
Near-inertial wave generation peaks in winter \citep[e.g.,][]{alford2003}, but
those waves project onto large horizontal scales \citep[e.g, ][]{qi_etal1995}.

>>>>

\cite{dasaro1978} showed that the velocity of linear internal waves
in the mixed layer strongly depends on the density jump at the mixed layer
base, with largest mixed layer velocities when the jump is strongest.
In summer, the shallow mixed layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape of the baroclinic modes
changes seasonally. In particular the baroclinic modes are
significantly more surface intensified in late summer/early fall
 (supplemental material).
If the internal wave source has weak seasonal dependence, then a strong
seasonal cycle in the near-surface expression of internal waves is expected.
Internal tide generation does not show a seasonal modulation \citep[e.g.,][]{alford2003},
and therefore one expects a strong seasonality in the near-surface
expression of internal tides and
other submesoscale inertia-gravity waves generated through internal tide interactions.
Near-inertial wave generation peaks in winter \citep[e.g.,][]{alford2003}, but
those waves project onto large horizontal scales \citep[e.g, ][]{qi_etal1995}.
